Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-17 paper.qmd
Updated PBMC3k projections

@@

>>>>

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1.23, 
               scaled_data = scaled_pbmc_data, 
               scaled_data_model = scaled_pbmc_data_model, 
               distance_df_small_edges = distance_df_small_edges_pbmc, 
               axis_param = list(limits = 1, 
                                 axis_pos_x = -0.48, 
                                 axis_pos_y = -0.48, 
                                 threshold = 0.082))

projected_df <- proj_obj1$projected_df
model_df <- proj_obj1$model_df
axes <- proj_obj1$axes
circle <- proj_obj1$circle

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 1.25, 
               scaled_data = scaled_pbmc_data, 
               scaled_data_model = scaled_pbmc_data_model, 
               distance_df_small_edges = distance_df_small_edges_pbmc, 
               axis_param = list(limits = 1.35, 
                                 axis_pos_x = -0.75, 
                                 axis_pos_y = -0.75, 
                                 threshold = 0.12))

projected_df <- proj_obj2$projected_df
model_df <- proj_obj2$model_df
axes <- proj_obj2$axes
circle <- proj_obj2$circle
